An Example Using the Tufte Style

### 2016-10-16 lists_conversion_experience.rmd
slide work
playing with formats

@@

```{r biscuits, echo=FALSE, cache=TRUE}
    library(dplyr)
    library(ggplot2)
    library(readr)
    bisc = read_tsv('data/biscuits.csv')
    bisc %>% select(price, name)  %>% order(price, decreasing=TRUE)    
    bisc[order(bisc$price, decreasing=TRUE), c('name','price')]
```
We can imagine this in terms of biscuits.

>>>>

---
title: "An Example Using the Tufte Style"
author: "John Smith"
output:
  tufte::tufte_handout: default
tufte::tufte_html: default
---

@@

```{r biscuits, echo=FALSE, cache=TRUE}
    library(dplyr)
    library(ggplot2)
    library(readr)
    bisc = read_tsv('data/biscuits.csv')
    bisc[order(bisc$price, decreasing=TRUE), c('name','price')]
```
We can imagine this in terms of biscuits.
